Generating Simulated Data

### 2021-03-26 docs/SimData.Rmd
some vbgf fits work but many are strange check data

    #dplyr::group_by(species, era) %>%
    #group_map(try(~nls(length~vb1(avgage, Linf, K, t0), data = .,
    #              start = vbStarts(length~avgage,data = .))))

>>>>

    saithe1 <- svlenage %>%
      filter(species=="Saithe",
             era==1)

    nls(length~vb1(avgage, Linf, K, t0), data = saithe1,
                  start = vbStarts(length~avgage,data = saithe1))
#Nonlinear regression model
#   model: length ~ vb1(avgage, Linf, K, t0)
#    data: saithe1
#      Linf         K        t0 
# 388.18797   0.01975  -3.94798 
#  residual sum-of-squares: 5691213
# 
# Number of iterations to convergence: 5 
# Achieved convergence tolerance: 5.511e-06

 svvbgf <- svlenage %>%   
    dplyr::group_by(species) %>%
    group_map(~try(nls(length~vb1(avgage, Linf, K, t0), data = .,
                  start = vbStarts(length~avgage,data = .))))

 svvbgf2 <- svlenage %>%   
    dplyr::group_by(species) %>%
    group_modify(~broom::tidy(possibly(nls(length~vb1(avgage, Linf, K, t0), data = .x,
                  start = vbStarts(length~avgage,data = .x)), otherwise = NA_real_)))
 svvbgf3 <- svlenage %>%   
    dplyr::group_by(species, era) %>%
    group_map(~try(nls(length~vb1(avgage, Linf, K, t0), data = .,
                  start = vbStarts(length~avgage,data = .))))
